Optimized Synthesized Spectrum

### 2016-10-02 2016.10.3 Jason_v2.tex
Update 2016.10.3 Jason_v2.tex

There are some tricks in the fitting. Because the fitting module is very sensitive to the outliers in the spectrum data, we add a constant to the flux and subtract it after the fitting. The result is better because a+b+c is closer to 1, which is 0.996 compared to 0.983.
\bigskip
Also, we add a bound to the parameters to make b is bigger than a or c. set the range of b as (0.8,1.2)

@@

The result is \(a+b+c = 0.997\). (a,b,c) = (-0.005,0.810, 0.192)

>>>>

@@

The result is \(a+b+c = 0.982\). (a,b,c) = ()
